\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
tweaked some wording
some comments in section V

%\long\def\commentp#1{}
%\long\def\commentpk#1{}
%\long\def\commentm#1{}
%\long\def\commentd#1{}

@@

Currently agents cannot switch lanes. AORTA allows merging lanes by treating
the merge point as an intersection. \commentpk{i take it this is an orphan
paragraph?} \commentd{yeah, where should it belong?}

@@

\begin{enumerate}
  \item Introduces new agents into the map
  \item Updates the position and velocity of agents based on their choice of
        acceleration in the previous step
  \item Checks for collisions
  \item Allows each agent to choose an action for the next step
\end{enumerate}

@@

Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system with
zero initial speed. Because behaviors must enforce speed limit along a lane
from the moment an agent enters a road, it is safe for a new agent to enter a
road if there is no other agent within the worst-case distance (traveling
distance at the speed limit, plus stopping distance from this speed) preceeding
the spawn point.% To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

All traversables (lanes and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. One simulation step happens atomically,
meaning collision checking occurs after all agents have moved. If this were not
the case, false positives could occur when an agent steps before the agent in front
of it. A collision is defined as the reversal of order of agents during a step.

@@

\subsection{Agent Reactions}
\label{sec:behaviors}

Each agent has a \emph{behavior} governing it, responsible for obeying
intersection policies and avoiding collisions. When the agent travels past the
end of a lane during its step, the behavior picks the turn to take. At each
step, the behavior can make the agent react by performing one of two actions:
disappearing from the map (when the agent is at rest and is done with its route)
or setting an acceleration for the next step. Were lane changing modeled, that
would be another possible action.

@@

>>>>

% \long\def\commentp#1{}
% \long\def\commentpk#1{}
% \long\def\commentm#1{}
% \long\def\commentd#1{}

@@

Currently agents cannot switch lanes. AORTA allows merging lanes by treating
the merge point as an intersection. \commentpk{move this to the limitations
section, and rename the section to "Current limitations". Explain gridlock as a
main limitation, and put this in somewhere}

@@

\begin{enumerate}
  \item Introduces new agents into the map
  \item Updates the position and velocity of agents based on their choice of
        acceleration in the previous step
  \item Checks for collisions
  \item Allows each agent's behavior to choose an action for the next step
\end{enumerate}

@@

Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system with
zero initial speed. \commentpk {For space, remove the following sentence as well, and merge this paragraph into thr previous one} Because behaviors must enforce speed limit along a lane
from the moment an agent enters a road, it is safe for a new agent to enter a
road if there is no other agent within the worst-case distance (traveling
distance at the speed limit, plus stopping distance from this speed) preceeding
the spawn point. % To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

All traversables (lanes and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. \commentpk{remove the following 2 sentences} One simulation step happens atomically,
meaning collision checking occurs after all agents have moved. If this were not
the case, false positives could occur when an agent steps before the agent in front
of it. A collision is defined as the reversal of order of agents during a step. \commentpk{maybe change this to "A collision is detected as the reversal of order of agents after a time step has completed. Also do we still have point vehicles only?}

@@

\subsection{Agent Behavior}
\label{sec:behaviors}

Each agent has a \emph{behavior} governing it, responsible for obeying
intersection policies and avoiding collisions. When the agent travels past the
end of a lane during its step, the behavior picks the turn to take. At each
step, the behavior can make the agent react by performing one of two actions:
disappearing from the map (when the agent is at rest and is done with its route)
or setting an acceleration for the next step. Were lane changing modeled, that
would be another possible action. \commentpk {remove last line - we'll bundle it up in limitations}

@@

\commentpk{The last 2 paragraphs need to move into the configurability section, as they are not part of the simulator directly. Similarly there should be a subsection on intersection behaviors here}
